Timely Object Recognition

### 2012-11-03 writeups/nips12/technical.tex
small change

Additionally, we include the mean and maximum entropy of class presence and time features that represent the times until start and deadline, for a total of $F = 1+|K|*2+6$ features.

>>>>

Additionally, we include the mean and maximum entropy of class presence and time features that represent the times until start and deadline, for a total of $F = 1+2K+6$ features.
